\Large Feature and order manipulations in a free recall task affect memory for current and future lists

### 2023-11-18 paper/main.tex
edits through end of methods section

Probability of first recall curves~\citep{AtkiShif68, PostPhil65, WelcBurn24}
reflect the probability that an item will be recalled first, as a function of
its serial position during encoding. We used an analogous approach to compute
the proportion of trials on which each item (as a function of its presentation
position) was recalled at output position $n$~\citep{Hoga75, HowaKaha99,
PolyEtal09, ZhanEtal23}. To carry out this analysis, we initialized (for each
participant) a number-of-lists (16) by number-of-words-per-list (16) matrix of
0s. Then, for each list, we found the index of the word that was recalled
first, and we filled in that position in the matrix with a 1. Finally, we
averaged over the rows of the matrix to obtain a 1 by 16 array of
probabilities, for each participant. We used an analogous procedure to compute
probability of $n$\textsuperscript{th} recall curves for each participant.
Specifically, we filled in the corresponding matrices according to the
$n$\textsuperscript{th} recall on each list that each participant made. When a
given participant had made fewer than $n$ recalls for a given list, we simply
excluded that list from our analysis when computing that participant's
curve(s). The probability of first recall curve corresponds to a special case
where $n = 1$.

@@

The lag-conditional response probability (lag-CRP) curve~\citep{Kaha96}
reflects the probability of recalling a given item after the just-recalled
item, as a function of their relative encoding positions (lag). In other words,
a lag of 1 indicates that a recalled item was presented immediately after the
previously recalled item, and a lag of $-3$ indicates that a recalled item came
three items before the previously recalled item. For each recall transition
(following the first recall), we computed the lag between the just-recalled
word's presentation position and the next-recalled word's presentation
position. We computed the proportions of transitions (between successively
recalled words) for each lag, normalizing for the total numbers of possible
transitions. In carrying out this analysis, we excluded all incorrect recalls
and repetitions (i.e., recalling a word that had already appeared previously in
the current recall sequence). This yielded, for each list, a 1 by
number-of-lags ($-15$ to $+15$; 30 lags in total, excluding lags of 0) array of
conditional probabilities. We averaged these probabilities across lists to
obtain a single lag-CRP for each participant. Because transitions at large
absolute lags are rare, these curves are typically displayed using range
restrictions~\citep{Kaha12}.

@@

All of the data analyzed in this manuscript, along with all of the code for
carrying out the analyses may be found at https://github.com/ContextLab/FRFR-analyses.

@@

All of the data analyzed in this manuscript, along with all of the code for
carrying out the analyses may be found at
https://github.com/ContextLab/FRFR-analyses. Code for running the non-adaptive
experimental conditions may be found at
https://github.com/Con\-text\-Lab/efficient-learning-code. Code for running the
adaptive experimental condition may be found at
https://github.com/ContextLab/adaptiveFR. We have also released an associated
Python toolbox for analyzing free recall data, which may be found at
https://cdl-quail.read\-the\-docs.io/\-en/\-latest/.  Note that this study was not
preregistered.  Some of the ideas and data presented in this manuscript
were also presented at the Annual Meeting of the Society for Neuroscience (2017).

>>>>

Probability of first recall curves~\citep{AtkiShif68, PostPhil65, WelcBurn24}
reflect the probability that an item will be recalled first, as a function of
its serial position during encoding. We used an analogous approach to compute
the proportion of trials on which each item (as a function of its presentation
position) was recalled at each output position $n$~\citep{Hoga75, HowaKaha99,
PolyEtal09, ZhanEtal23}. To carry out this analysis, we initialized (for each
participant) a number-of-lists (16) by number-of-words-per-list (16) matrix of
0s. Then, for each list, we found the presentation index of the word that was recalled
first, and filled in that position in the matrix with a 1. Finally, we
averaged over the rows of the matrix to obtain a 1 by 16 array of
probabilities, for each participant. We used an analogous procedure to compute
probability of $n$\textsuperscript{th} recall curves for each participant.
Specifically, we filled in the corresponding matrices according to the
$n$\textsuperscript{th} recall on each list that each participant made. When a
given participant had made fewer than $n$ recalls for a given list, we simply
excluded that list from our analysis when computing that participant's
curve(s). The probability of first recall curve corresponds to a special case
where $n = 1$.

@@

The lag-conditional response probability (lag-CRP) curve~\citep{Kaha96}
reflects the probability of recalling a given item after the just-recalled
item, as a function of the items' relative encoding positions (lag). In other words,
a lag of 1 indicates that a recalled item was presented immediately after the
previously recalled item, and a lag of $-3$ indicates that a recalled item came
three items before the previously recalled item. For each recall transition
(following the first recall), we computed the lag between the presentation positions
of the just-recalled word and the next-recalled word. 
We then computed the proportions of transitions (between successively
recalled words) for each lag, normalizing for the total numbers of possible
transitions. In carrying out this analysis, we excluded all incorrect recalls
and repetitions (i.e., recalling a word that had already appeared in
the current recall sequence). This yielded, for each list, a 1 by
number-of-lags ($-15$ to $+15$; 30 lags in total, excluding lags of 0) array of
conditional probabilities. We averaged these probabilities across lists to
obtain a single lag-CRP for each participant. Because transitions at large
absolute lags are rare, these curves are typically displayed using range
restrictions~\citep{Kaha12}.

@@

All of the data analyzed in this manuscript, along with all of the code for
carrying out the analyses, may be found at https://github.com/ContextLab/FRFR-analyses.
Code for running the non-adaptive
experimental conditions may be found at
https://github.com/Con\-text\-Lab/efficient-learning-code. Code for running the
adaptive experimental condition may be found at
https://github.com/ContextLab/adaptiveFR. We have also released an associated
Python toolbox for analyzing free recall data, which may be found at
https://cdl-quail.read\-the\-docs.io/\-en/\-latest.

@@

All of the data analyzed in this manuscript, along with all of the code for
carrying out the analyses may be found at
https://github.com/ContextLab/FRFR-analyses. Code for running the non-adaptive
experimental conditions may be found at
https://github.com/Con\-text\-Lab/efficient-learning-code. Code for running the
adaptive experimental condition may be found at
https://github.com/ContextLab/adaptiveFR. We have also released an associated
Python toolbox for analyzing free recall data, which may be found at
https://cdl-quail.read\-the\-docs.io/\-en/\-latest.  Note that this study was not
preregistered.  Some of the ideas and data presented in this manuscript
were also presented at the Annual Meeting of the Society for Neuroscience (2017)
and the Context and Episodic Memory Symposium (2017).
